Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-09-06 Chapter_0/04_Manuscript/Manuscript.tex
Worked on revision

\noindent 4. Differences in permeability were mainly caused by different degrees
of human activities across regions, which hampered dispersal. Rivers, swamps  or
open water also limited dispersal, while other landscape features had a limited
effect.

@@

\subsection{GPS Relocation Data}
We used a population of free-ranging African wild dogs inhabiting the Okavango
Delta in northern Botswana as a source population for dispersing individuals.
This population has been extensively studied since 1989 \citep{McNutt.1996,
Cozzi.2013, Cozzi.2020, Behr.2020}. Between 2011 and 2019, we systematically
collected GPS relocation data on 16 coalitions of dispersing African wild dogs
(7 female and 9 male coalitions). Candidate dispersing individuals were
identified based on age, number of same‐sex siblings, pack size, and presence of
unrelated individuals of the opposite sex in ther pack citep \citep{McNutt.1996,
Behr.2020}\todo{We originally only pointed to Behr and did not include the
criteria. The editor desired to include those}. Individuals were immobilized
according to protocols described in \cite{Osofsky.1996}, and fitted with
GPS/Satellite radio collars (\textit{Vertex Lite; Vectronic Aerospace GmbH,
Berlin, Germany}) while still with their natal pack. All procedures were
undertaken and supervised by a Botswana-registered wildlife veterinarian. Fully
assembled collars produced a tag weight of approximately 330 g, accounting for
approximately 1.2\% of a wild dog's average body weight. Collars were mounted
using leather belts and included a drop off mechanism, triggered by a slowly
decomposing piece of cloth.\todo{Editor desired more information on GPS collar}
During dispersal, GPS collars were programmed to record GPS relocation data
every 4 hours and to regularly transmit them via Iridium satellite system to a
base station.

@@

\noindent The selection score \(w(x)\) of a step depended on its associated
covariates (\(x_1, x_2, ..., x_n\)), as well as on the animal's relative
selection strength \todo{As per reviewer 1} for these covariates (\(\beta_1,
\beta_2, ..., \beta_n\)). To estimate relative selection strengths \todo{As per
reviewer 1} (i.e. the \(\beta\)'s), we used mixed effects conditional logistic
regression analysis as suggested by \cite{Muff.2020}. We implemented their
method using the R-package \textit{glmmTMB} \citep{Mollie.2017} and used
dispersing coalition ID to model random slopes. We also modelled random
intercepts with an arbitrary high variance of 10\textsuperscript{6} to make use
of the poisson trick (see \citealp{Muff.2020}). We defined three movement
metrics, namely the cosine of the turning angle (\(cos(ta)\)), the step length
(\(sl\)) and the natural logarithm of the step length (\(log(sl)\)), as core
covariates and ran stepwise forward model selection based on Akaike's
Information Criterion (AIC; \citealp{Burnham.2002}) for all other
covariates.\todo{Reviewer 1 asked for more details in the random effects. I
therefore decided to update this section too} The inclusion of movement metrics
served to reduce biases in estimated habitat selection coefficients \todo{as per
revierwer 1} that may have arisen due to movement behavior \citep{Avgar.2016}.
To validate the predictive power of the most parsimonious habitat selection
model, we ran k-fold cross-validation for case-control studies as described in
\cite{Fortin.2009} (details in Appendix A.5).

>>>>

\noindent 4. Differences in permeability were mainly related to different
degrees of human activities across regions, as well as to the presence of
rivers, swamps or open water. The relation between other landscape features and
landscape permeability was less evident.\todo{Editor indicated that the
relationships are correlative and not necessarily causal.}

@@

\subsection{GPS Relocation Data}
We used a population of free-ranging African wild dogs inhabiting the Okavango
Delta in northern Botswana as a source population for dispersing individuals.
This population has been extensively studied since 1989 \citep{McNutt.1996,
Cozzi.2013, Cozzi.2020, Behr.2020}. Between 2011 and 2019, we systematically
collected GPS relocation data on 16 coalitions of dispersing African wild dogs
(7 female and 9 male coalitions). Candidate dispersing individuals were
identified based on age, number of same‐sex siblings, pack size, and presence of
unrelated individuals of the opposite sex in ther pack citep \citep{McNutt.1996,
Behr.2020}\todo{We originally only pointed to Behr and did not include the
criteria. The editor desired to include those}. Individuals were immobilized
according to protocols described in \cite{Osofsky.1996}, and fitted with
GPS/Satellite radio collars (\textit{Vertex Lite; Vectronic Aerospace GmbH,
Berlin, Germany}) while still with their natal pack. All procedures were
undertaken and supervised by a Botswana-registered wildlife veterinarian.
Collars produced a tag weight of 1.2\% of a wild dog's average body weight,
which is well within published recommendations \citep{Kenward.2000}. Collars
were attached through a leather belt that included a drop off mechanism,
triggered by a slowly decomposing piece of cloth.\todo{Editor desired more
information on GPS collar} During dispersal, GPS collars were programmed to
record GPS relocation data every 4 hours and to regularly transmit them via
Iridium satellite system to a base station.

@@

\noindent The selection score \(w(x)\) of a step depended on its associated
covariates (\(x_1, x_2, ..., x_n\)), as well as on the animal's relative
selection strength \todo{As per reviewer 1} for these covariates (\(\beta_1,
\beta_2, ..., \beta_n\)). To estimate relative selection strength \todo{As per
reviewer 1} (i.e. the \(\beta\)'s) for each covariate, we used mixed effects
conditional logistic regression analysis as suggested by \cite{Muff.2020}. We
implemented their method using the R-package \textit{glmmTMB}
\citep{Mollie.2017} and used dispersing coalition ID to model random slopes. We
also modelled random intercepts with an arbitrary high variance of
10\textsuperscript{6} to make use of the poisson trick (see
\citealp{Muff.2020}). We defined three movement metrics, namely the cosine of
the turning angle (\(cos(ta)\)), the step length (\(sl\)) and the natural
logarithm of the step length (\(log(sl)\)), as core covariates and ran stepwise
forward model selection based on Akaike's Information Criterion (AIC;
\citealp{Burnham.2002}) for all other covariates.\todo{Reviewer 1 asked for more
details in the random effects. I therefore decided to update this section too}
The inclusion of movement metrics served to reduce biases in estimated habitat
selection coefficients \todo{as per revierwer 1} that may have arisen due to
movement behavior \citep{Avgar.2016}. To validate the predictive power of the
most parsimonious habitat selection model, we ran k-fold cross-validation for
case-control studies as described in \cite{Fortin.2009} (details in Appendix
A.5).
